\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\setheader{Acknowledgements}
\label{acknowledgements}

I would like begin by thanking my supervisor Prof. Kirk Atkinson for the significant impact he has had on my career, professional development, and my research interests. From hiring me as a research student over the summer of 2020, to supervising my capstone project in the final year of my undergraduate studies, and agreeing to take me on as a graduate student with a project that I had the ability to shape to my own interests; you have always supported me as I grew into academia. Even though you have been incredibly busy as of late, you've always taken the time to chat, provide feedback on my work, and encourage me to explore areas I'm interested in which are only tangentially related to my research project. I cannot thank you enough for everything you've done for me over the last four years.

I would like to acknowledge several other faculty members at Ontario Tech for providing guidance and support over the last few years. I would like to start with Prof. Markus Piro, thank you for agreeing to be on my supervisory committee. I appreciate how you've always made time to talk and provide advice regarding my work or career as a whole. Prof. John Froats, thank you for your mentorship through several teaching assistant positions. You've taught me what it means to be a nuclear professional. Prof. Rachid Machrafi, thank you for encouraging me to consider graduate studies. Without your advice, I would not be here today. 

Though it would be impossible to name them all, I wish to thank the many colleagues that I've met through my time here at Ontario Tech. To Amna Hassan, Scott McKay and Viridiana Borjas Padilla, thank you for listening to my rants and in general being the best lab mates one could want. I want to thank Daniel Chen, Graeme Francolini, Morgan Collins, Nicholas Somer, Nikolas Lymberis Scuro, and Tyra Gordon. I appreciate all of our conversations about both work and life, the many lunches and coffee breaks, and in general making graduate school at Ontario Tech a positive experience. We may have started out as colleagues, but I am proud to call you all my friends.

Lastly, I would like to thank my family and close friends for always being there for me. In particular, I want to thank my mother Aganetha, my father Cornelio, and my brother Alexander for pushing me to continue higher education and pursue my passions. To my good friends Adam, Charlie, Ethan, Luka, Nam, Nathan and Tommy, thank you for your patience whenever I waxed on about my research completely unsolicited. 

This research was undertaken thanks to funding provided by the University Network of Excellence in Nuclear Engineering (UNENE) and the Natural Sciences and Engineering Research Council of Canada (NSERC) through the Industrial Research Chairs program [funding reference number IRCPJ 549979-19]. 