\chapter*{Statement of Contributions}
\addcontentsline{toc}{chapter}{Statement of Contributions}
\setheader{Statement of Contributions}

I hereby certify that I am the sole author of this thesis. I have used standard referencing practices to acknowledge ideas, research techniques, or other materials that belong to others. Furthermore, I certify that I am the sole source of the creative works and/or inventive knowledge described in this thesis. The work presented in this thesis which has been published, or is in the process of being published, can be found below.

\noindent\textbf{First Collision Source}

The Self-Adjoint Scalar Flux first-collision source discussed in Section~\ref{solver:radiation_transport:sasf_point_source} will be submitted for publication in the Journal of Computational Physics. The author of this thesis was responsible for conceptualising the work, performing mathematical derivations, devising computational testing, generating results, and writing the manuscript. K.D. Atkinson revised the manuscript.

\noindent\textbf{Verification with the Proposed OTU Subcritical Assembly Facility}

A portion of the verification studies presented in Section~\ref{verification:radiation_transport_sn:subcritical} involving the proposed Ontario Tech subcritical assembly have been published as: \textbf{K.\ Sawatzky} and {K.\ D.\ Atkinson}, \textit{Verification of a CARIBOU-OpenMC Workflow for the Analysis of HTGR-Like Systems Using the Proposed Ontario Tech Subcritical Assembly}, \href{https://www.ans.org/meetings/physor2024/}{Proceedings of PHYSOR-2024, (San Francisco, California, USA), American Nuclear Society, 2024}. The author of this thesis was responsible for conceptualising the work, devising computational testing, generating results, and writing the manuscript. K.D. Atkinson revised the manuscript.